Conference Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2023-05-14 LARS_paper/paper.tex
Fix spellings

In order to assess the robot's locomotion performance with the implemented stabilization controller, the robot's capability of following a forward velocity setpoint and the oscillation of its body while walking were evaluated. An experiment was conducted, in which the robot should walk in a straight line of 1.5 meters in both flat and irregular terrain, with and without the stabilization controller, totalizing four tests. The flat terrain consisted of a cement floor and the irregular terrain, a ground formed by small loose stones. Both are illustrated in Figures \ref{fig:terreno_plano} and \ref{fig:terreno_irregular}, respectively. For each test, the robot received a forward velocity command of 0.05 m/s, and its mean velocity, as well as its pitch and roll oscillation, were recorded. The mean velocity was calculated based on the time it took to travel 1.5 meters and the oscillation is the difference between the maximum and minimum readings of the IMU. The calculated velocity was compared to the desired velocity sent to the robot and the stability data was analyzed statistically: first, the Shapiro-Wilk test was applied to the distribution to check whether the distribution was normal; lastly, the results were compared by performing an analysis of variance (ANOVA). For all the tests, the robot's gait settings consisted of a height of 5 cm, a period of 0.5 seconds, a resolution of 25 points, $P_T$ = 0.66, and $P_N$ = 0.33. For each test type, 10 samples were collected.

@@

Table \ref{tab:vel_stab} summarizes the collected results. The robot did not reach a velocity of 0.05 m/s in any test. This result is due to errors in the final position of each leg during the swing phase: the legs could not reach the desired $(x,y)$ position required to maintain the desired velocity. The fact that the final position of one foot is a function of its motors' final orientation, indicates that the motors did not reach their desired orientation. Prior to the experiment, the gait movement was tested with the legs off the ground (almost no load), and no significant errors were noted. Since the errors only appeared while walking, it is perhaps caused by the fact that the motors were not powerful enough to support the robot's weight appropriately while walking.

@@

This paper addressed the design, prototyping and testing of a quadruped robot. An experiment was held to assess the robot's walking performance. The results showed that the robot did not reach the desired velocity in any of the tests. This was due to errors during the gait's swing phase, likely caused by the external disturbances caused by the robot's weight. This disturbances were not compensated, because the gait trajectory traking is open-loop (only the indivual joint's controllers are closed-loop). In addition to that, it was passible to conclude that the implemented stabilization controller was able to lower the robot's body oscillations while walking in pitch and roll in both flat and irregular terrains.

Reviewing the robot's actuators is recommended for future work. Perhaps a model with more torque is required for a more precise control performance.

>>>>

To assess the robot's locomotion performance with the implemented stabilization controller, the robot's capability of following a forward velocity setpoint and the oscillation of its body while walking were evaluated. An experiment was conducted, in which the robot should walk in a straight line of 1.5 meters in both flat and irregular terrain, with and without the stabilization controller, totalizing four tests. The flat terrain consisted of a cement floor and the irregular terrain, a ground formed by small loose stones. Both are illustrated in Figures \ref{fig:terreno_plano} and \ref{fig:terreno_irregular}, respectively. For each test, the robot received a forward velocity command of 0.05 m/s, and its mean velocity, as well as its pitch and roll oscillation, were recorded. The mean velocity was calculated based on the time it took to travel 1.5 meters and the oscillation is the difference between the maximum and minimum readings of the IMU. The calculated velocity was compared to the desired velocity sent to the robot and the stability data was analyzed statistically: first, the Shapiro-Wilk test was applied to the distribution to check whether the distribution was normal; lastly, the results were compared by performing an analysis of variance (ANOVA). For all the tests, the robot's gait settings consisted of a height of 5 cm, a period of 0.5 seconds, a resolution of 25 points, $P_T$ = 0.66, and $P_N$ = 0.33. For each test type, 10 samples were collected.

@@

Table \ref{tab:vel_stab} summarizes the collected results. The robot did not reach a velocity of 0.05 m/s in any test. This result is due to errors in the final position of each leg during the swing phase: the legs could not reach the desired $(x,y)$ position required to maintain the desired velocity. The fact that the final position of one foot is a function of its motors' final orientation, indicates that the motors did not reach their desired orientation. Before the experiment, the gait movement was tested with the legs off the ground (almost no load), and no significant errors were noted. Since the errors only appeared while walking, it is perhaps caused by the fact that the motors were not powerful enough to support the robot's weight appropriately while walking.

@@

This paper addressed the design, prototyping and testing of a quadruped robot. An experiment was held to assess the robot's walking performance. The results showed that the robot did not reach the desired velocity in any of the tests. This was due to errors during the gait's swing phase, likely caused by the external disturbances caused by the robot's weight. These disturbances were not compensated, because the gait trajectory tracking is open-loop (only the individual joint's controllers are closed-loop). In addition to that, it was possible to conclude that the implemented stabilization controller was able to lower the robot's body oscillations while walking in pitch and roll in both flat and irregular terrains.

Reviewing the robot's actuators is recommended for future work. Perhaps a model with more torque is required for more precise control performance.
